\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
doc/paper.tex: add/correct cross-references

The next step is to write a substitute for
the low-energy boundary condition class.
It must be declared as a descendent of \code{Constraint<Two_scale>}:
% MSSMcbs_two_scale_low_scale_constraint.hpp
\begin{numlstlisting}
#include "two_scale_constraint.hpp"

@@

\subsection{Run-time comparison}

@@

For the run-time comparison we're generating $2\cdot 10^{4}$ random
CMSSM parameter points with $m_0\in [50,1000]\unit{GeV}$, $m_{1/2}\in
[50,1000]\unit{GeV}$, $\tan\beta\in [1,100]$, $\sign\mu\in \{-1,+1\}$
and $A_0\in [-1000,1000]\unit{GeV}$.  For each point an SLHA input
file is created by appending the values of $m_0$, $m_{1/2}$,
$\tan\beta$, $\sign\mu$, $A_0$ in form of a \code{MINPAR} block to the
SLHA template file given in
\secref{sec:speed-test-slha-template-file}.  The resulting SLHA input
file is passed to each spectrum generator and the (wall-clock) time is
measured until the program has finished.  The average run-times for
three different CPU types can be found in
\tabref{tab:run-time-comparison}.  The first column shows the run-time
on a Intel Core2 Duo (P8600, $2.40\unit{GHz}$) where only one core was
enabled.  The second column shows the run-time on the same processor
where both cores were enabled.  In the third column a Intel Xeon
(L5640, $2.27\unit{GHz}$) was used, which has $6$ CPU cores.
%
\begin{table}[tbh]
  \centering
  \begin{tabular}{llll}
    \toprule
                            & Intel Core2 Duo    & Intel Core2 Duo   & Intel Xeon\\
                            & (P8600, 1 core)    & (P8600, 2 cores)  & (L5640, 6 cores)\\
    \midrule
    FlexibleSUSY-NoFV 1.0.0 & $0.086\unit{s}$    & $0.079\unit{s}$   & $0.060\unit{s}$\\
    SPheno 3.2.4            & $0.119\unit{s}$    & $0.114\unit{s}$   & $0.101\unit{s}$\\
    Softsusy 3.4.0          & $0.175\unit{s}$    & $0.171\unit{s}$   & $0.147\unit{s}$\\
    \midrule
    FlexibleSUSY-FV 1.0.0   & $0.150\unit{s}$    & $0.113\unit{s}$   & $0.074\unit{s}$\\
    SPhenoMSSM 4.1.0        & $0.415\unit{s}$    & $0.401\unit{s}$   & $0.370\unit{s}$\\
    \bottomrule
  \end{tabular}
  \caption{Average run-time of CMSSM spectrum generators
    for random parameter points.  The first three rows show
    spectrum generators which disallow flavour violation.  Rows
    $4$--$5$ contain flavour violating spectrum generators, based
    on SARAH's MSSM model file.}
  \label{tab:run-time-comparison}
\end{table}

@@

We also compared the run-time of \fs against SPheno, Softsusy and the
SARAH generated MSSM spectrum generator SPhenoMSSM.  The test results
can be found in \secref{sec:comparison}.

>>>>

The next step is to write a substitute for
the low-energy boundary condition class.
It must be declared as a descendent of \code{Constraint<Two_scale>}
whose function is described in \secref{sec:boundary-conditions}:
% MSSMcbs_two_scale_low_scale_constraint.hpp
\begin{numlstlisting}
#include "two_scale_constraint.hpp"

@@

\subsection{Run-time comparison}
\label{sec:run-time comparison}

@@

For the run-time comparison we're generating $2\cdot 10^{4}$ random
CMSSM parameter points with $m_0\in [50,1000]\unit{GeV}$, $m_{1/2}\in
[50,1000]\unit{GeV}$, $\tan\beta\in [1,100]$, $\sign\mu\in \{-1,+1\}$
and $A_0\in [-1000,1000]\unit{GeV}$.  For each point an SLHA input
file is created by appending the values of $m_0$, $m_{1/2}$,
$\tan\beta$, $\sign\mu$, $A_0$ in form of a \code{MINPAR} block to the
SLHA template file given in
\ref{sec:speed-test-slha-template-file}.  The resulting SLHA input
file is passed to each spectrum generator and the (wall-clock) time is
measured until the program has finished.  The average run-times for
three different CPU types can be found in
\tabref{tab:run-time-comparison}.  The first column shows the run-time
on a Intel Core2 Duo (P8600, $2.40\unit{GHz}$) where only one core was
enabled.  The second column shows the run-time on the same processor
where both cores were enabled.  In the third column a Intel Xeon
(L5640, $2.27\unit{GHz}$) was used, which has $6$ CPU cores.
%
\begin{table}[tbh]
  \centering
  \begin{tabular}{llll}
    \toprule
                            & Intel Core2 Duo    & Intel Core2 Duo   & Intel Xeon\\
                            & (P8600, 1 core)    & (P8600, 2 cores)  & (L5640, 6 cores)\\
    \midrule
    FlexibleSUSY-NoFV 1.0.0 & $0.086\unit{s}$    & $0.079\unit{s}$   & $0.060\unit{s}$\\
    SPheno 3.2.4            & $0.119\unit{s}$    & $0.114\unit{s}$   & $0.101\unit{s}$\\
    Softsusy 3.4.0          & $0.175\unit{s}$    & $0.171\unit{s}$   & $0.147\unit{s}$\\
    \midrule
    FlexibleSUSY-FV 1.0.0   & $0.150\unit{s}$    & $0.113\unit{s}$   & $0.074\unit{s}$\\
    SPhenoMSSM 4.1.0        & $0.415\unit{s}$    & $0.401\unit{s}$   & $0.370\unit{s}$\\
    \bottomrule
  \end{tabular}
  \caption{Average run-time of CMSSM spectrum generators
    for random parameter points.  The first three rows show
    spectrum generators which disallow flavour violation.  Rows
    $4$--$5$ contain flavour violating spectrum generators, based
    on SARAH's MSSM model file.}
  \label{tab:run-time-comparison}
\end{table}

@@

We also compared the run-time of \fs against SPheno, Softsusy and the
SARAH generated MSSM spectrum generator SPhenoMSSM.  The test results
can be found in \secref{sec:run-time comparison}.
